Supporting information

### 2019-09-03 EAshiklomanovSA2.Rmd
Add Figure S1 (comparison of all means)

>>>>

```{r mean-compare-all, echo = FALSE, fig.cap = mca_cap}
mca_cap <- paste(
  "Mean and 95% credible intervals on estimates of trait means for each plant functional type",
  "from the univariate, multivariate, and hierarchical models.",
  "For leaf lifespan and SLA, results were similar for mass- and area-based models,",
  "so only results from the mass-based model area shown.",
  "For some PFT-trait combination, where error bars are large due to the relatively",
  "uniformative prior, $y$ axes are constrained to facilitate comparison."
)
knitr::include_graphics(file.path(npdir, "figures", "manuscript", "mean_comparison_all.pdf"))
```
